\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Marcus Vinicius Aloise Teixeira} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+55(69) 984492828 \\ Porto Velho(RO), Brazil} 
\address{\href{mailto:contact@faangpath.com}{marcusaloise@gmail.com} \\ \href{https://www.linkedin.com/in/marcusaloise/}{linkedin.com/marcusaloise/} \\ \href{https://github.com/marcusaloise/}{github.com/marcusaloise/}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Site Reliability Engineer with 1 years of experience in 2022, seeking full-time Devops/SRE roles.

Passionate about technology. Currently completing my degree in Information Systems at Cruzeiro do Sul, self-taught professional, continually improving my skills.

I have experience in several tools, with a solid foundation in automation, cloud services and systems monitoring. I am certified AWS Certified Cloud Practitioner and have practical experience with Ansible, Docker, Kubernetes.

}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, Cruzeiro do Sul \hfill {2021 - 2025}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, Golang, Bash \\
DevOps Tools & Ansible, Terraform, Docker, Kubernetes, GitHub Actions \\
Cloud Platforms &  AWS (Certified) \\
Monitoring Tools & Zabbix, New Relic, Prometheus, Grafana \\
Database Management & MySQL \\ 
Networking and Security &  OWASP Top 10, Wireshark/tcpdump, Trivy \\

\\
Soft Skills & Self-taught, Organized, Flexibility, Planning, Learning Mindset, Communicative. \\

\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Devops Engineer - intern} \hfill Jan 2024 \\
Tribunal de Justiça \hfill \textit{Porto Velho, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Installation and configuration of bare metal servers.
     \item Deploy applications using docker.
    \item Creation of ansible playbook to automate configuration of Rhel machines. 
 \end{itemize}
 
\textbf{Noc - intern} \hfill Jun 2023 - Jan 2024\\
BRasil Digital Telecom \hfill \textit{Porto Velho, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Creation of ansible playbook to automate configuration of virtual machines.
     \item Treatment of bases in relational databases and creation of dashboards using Power BI.
    \item Creation of automated query microservices (api) using Python. 
    \item Installing and configuring new relic (Observability)
 \end{itemize}
 
\textbf{Site Reliability Engineer} \hfill Jun 2022 - feb 2023\\
C6 Bank \hfill \textit{São Paulo, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Vulnerability management and treatment in AWS.
     \item Creation of IAC for automation testing.
    \item Script development for process automation.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS} 
\vspace{-1.25em}
\item \textbf{Server Connection Tool.} Developed ``server\_connections.sh,'' a bash script that simplifies the process of connecting to on-premise servers at my current company. By utilizing ``servers.conf,'' a configuration file, the script lists and automatically connects to servers via SSH, eliminating the need for repeated password entries. This tool has significantly enhanced the efficiency of remote server access.

\item \textbf{GitHub Actions and AWS Deployment:} Developed an automated deployment process using ``GitHub Actions'' to update a personal website hosted on AWS S3. The process triggers upon a push to the main branch, deploying the latest version of the site automatically. This setup not only streamlines updates but also integrates ``servers.conf,'' a configuration file that aids in managing deployments. Such automation has substantially increased the efficiency of maintaining and updating the site, making it an excellent showcase of practical CI/CD principles in action.

\item \textbf{Kubernetes Cluster Implementation:} Successfully set up a Kubernetes cluster independently using ``kubeadm'' for cluster management and ``metallb'' as a load balancer to expose services externally. This project involved configuring multiple nodes, ensuring high availability, and implementing network policies to secure inter-pod communication. The deployment of this cluster demonstrates proficiency in key Kubernetes concepts and tools, significantly enhancing the scalability and reliability of containerized applications.

\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	I volunteer at a local church to do live streaming 
    \item	Calisthenics athlete.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
